Data Preparation

### 2019-01-10 Data Preparation.Rmd

We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview_tidy <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

d_description_tidy <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)
print(d_description_tidy)
```

>>>>

We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

d_description <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)
print(d_description_tidy)
```
